A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
We're not the first to do this
We are good

\paragraph{Large subgraph isomorphism instances} We also ran the algorithms on
a set of 5,725 larger instances used in recent studies of subgraph
isomorphism~\citep{DBLP:conf/lion/KotthoffMS16} and maximum common
subgraph~\citep{UpcomingAAAIPaper}.  This benchmark set includes real-world
graphs and graphs generated using random models.  Pattern graphs range from 4
vertices to 900 with a median of 80; target graphs range from 10 vertices to
6,671 with a median of 561. Cumulative runtimes on these instances are shown in
\cref{figure:sip-cumulative}.  This is a challenging set of instances, and more
than half of the instances cannot be solved within a timeout of 1,000 seconds by
any solver. Furthermore, the CP-FC algorithm and the clique encoding run out of
memory on many of the instances (these are treated as timeouts).

The basic \McSplit\ is beaten by the $k{\downarrow}$ algorithm of
\citet{UpcomingAAAIPaper} on this dataset. However, we can modify the \McSplit\
algorithm to use a top-down strategy similar to that used by $k{\downarrow}$  by
calling the main \FuncSty{McSplit} method once per goal size ($g, g-1, g-2,
\dots$); we backtrack (\lineref{PruneSearch} of \cref{McSplitAlg}) when the
bound is strictly less than the goal size, and terminate when a solution of the
goal size is found. We expect that this could do well because in many cases the
matching covers nearly all of the smaller graph---indeed,
\cref{figure:sip-cumulative} shows that this approach is the strongest on these
instances.

>>>>

\paragraph{Large subgraph isomorphism instances} We also ran the algorithms on
a set of 5,725 larger instances used in recent studies of subgraph
isomorphism~\citep{DBLP:conf/lion/KotthoffMS16} and maximum common
subgraph~\citep{UpcomingAAAIPaper}.  This benchmark set includes real-world
graphs and graphs generated using random models.  Pattern graphs range from 4
vertices to 900 with a median of 80; target graphs range from 10 vertices to
6,671 with a median of 561. Cumulative runtimes on these instances are shown in
\cref{figure:sip-cumulative}.  This is a challenging set of instances, and more
than half of the instances cannot be solved within a timeout of 1,000 seconds by
any solver. Furthermore, the CP-FC algorithm and the clique encoding run out of
memory on many of the instances (these are treated as timeouts, following
\citet{UpcomingAAAIPaper}).

The basic \McSplit\ is beaten by the $k{\downarrow}$ algorithm of
\citet{UpcomingAAAIPaper} on this dataset. However, we can modify the \McSplit\
algorithm to use a top-down strategy similar to that used by $k{\downarrow}$  by
calling the main \FuncSty{McSplit} method once per goal size ($g, g-1, g-2,
\dots$); we backtrack (\lineref{PruneSearch} of \cref{McSplitAlg}) when the
bound is strictly less than the goal size, and terminate when a solution of the
goal size is found. We expect that this could do well because in many cases the
matching covers nearly all of the smaller graph---indeed,
\cref{figure:sip-cumulative} shows that this approach is the strongest on these
instances, and \McSplit{$\downarrow$} is the best algorithm for every choice of timeout.
